Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-06-27 sattose/paper.tex
Fixed T2R threshold

\begin{itemize}
  \item \textbf{Considering types:} Type 2 clones do not consider types. However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts. Because of this, we propose that type 2R clones should consider types like type 1R clones do.
  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account. We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables. For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}. Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account. We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter. However, we would argue that thresholds matter here. How many literals may differ for the segment still to be considered a clone with another segment? We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary. However, because of this, completely different methods can be called in cloned fragments as a result. This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code. This is because different method identifiers can describe a completely different functionality. Therefore, we suggest considering the call signatures of cloned methods when they are compared. We can allow variability in the rest of method identifiers by passing the function as a parameter. To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
\end{itemize}

>>>>

\begin{itemize}
  \item \textbf{Considering types:} Type 2 clones do not consider types. However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts. Because of this, we propose that type 2R clones should consider types like type 1R clones do.
  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account. We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables. For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}. Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account. We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter. However, we would argue that thresholds matter here. How many literals may differ for the segment still to be considered a clone with another segment? We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design. This threshold is displayed in equation \ref{eq:type2r}.
  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary. However, because of this, completely different methods can be called in cloned fragments as a result. This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code. This is because different method identifiers can describe a completely different functionality. Therefore, we suggest considering the call signatures of cloned methods when they are compared. We can allow variability in the rest of method identifiers by passing the function as a parameter. To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
\end{itemize}

\begin{equation}\label{eq:type2r}
\text{T2R}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100
\end{equation}
$$Diff = \text{Number that differ from other clone instances}$$
$$Total = \text{Total number in the clone instance}$$
$$l = \text{Literals in clone}$$
$$v = \text{Variables in clone}$$
$$m = \text{Method calls in clone}$$
$$t = \text{Tokens in clones}$$
